Presentation Title

### 2017-08-23 thesis/chapters/ch5-implementation.tex
Rearrange figures; edit

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-communication-cost-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-comms-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-communication-cost-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-comms-random}
    \end{subfigure}%
  }
  \caption{Experimental result of the communication cost per round for the consensus protocol.
  The error bars are larger for higher population size or higher number of facilitators is because rounds take longer thus they are repeated fewer times.}
  \label{fig:round-comms}
\end{figure}

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-duration-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-duration-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-duration-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-duration-random}
    \end{subfigure}%
  }
  \caption{Experimental result of the round duration per round for the consensus protocol.}
  \label{fig:round-duration}
\end{figure}

\Cref{fig:round-comms} shows the relationship between the communication cost of the consensus protocol per round and the population size.
The most important aspect is that these results show a linear increase,
which reinforces our analytical result in~\Cref{sec:cons-complexity}.
Note that regardless of whether the transactions are performed with a random neighbour or with a fixed neighbour,
the magnitude of the communication cost is similar.
Both peak at about 100 MB,
which is expected because the consensus protocol is decoupled from the transaction protocol and the validation protocol.
Finally, the rate for which the communication cost increases is higher when the number of facilitators is higher,
which is also expected because the ACS algorithm has a polynomial term w.r.t. $n$ in its communication complexity.

@@

\section{Linear global throughput}
\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/throughput-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/throughput-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput increases as the population increases when every node transact at the same rate.
  Using fixed neighbours results in a higher throughput because of the caching mechanism.}
  \label{fig:global-throughput}
\end{figure}

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/timeseries}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:backlog-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/timeseries}
    \caption{Transactions are with random neighbours.}
    \label{fig:backlog-random}
  \end{subfigure}
  }
  \caption{Demonstration of the network bottleneck.
  Note that the slope of validated transactions grows at a slower rate in~\Cref{fig:backlog-random} than in~\Cref{fig:backlog-fixed}.}
  \label{fig:backlog}
\end{figure}

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/round-communication-cost-vs-facilitators}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:facilitators-round-comms-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/round-communication-cost-vs-facilitators}
    \caption{Transactions are with random neighbours.}
    \label{fig:facilitators-round-comms-random}
  \end{subfigure}
  }
  \caption{The communication cost of the consensus protocol increases polynomially with respect to the number of facilitators as expected from the ACS communication complexity.}
  \label{fig:facilitators-round-comms}
\end{figure}

@@

>>>>

\afterpage{
\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-communication-cost-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-comms-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-communication-cost-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-comms-random}
    \end{subfigure}%
  }
  \caption{Experimental result of the communication cost per round for the consensus protocol.
  The error bars are larger for higher population size or higher number of facilitators is because rounds take longer thus they are repeated fewer times.}
  \label{fig:round-comms}
\end{figure}

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-duration-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-duration-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-duration-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-duration-random}
    \end{subfigure}%
  }
  \caption{Experimental result of the round duration per round for the consensus protocol.}
  \label{fig:round-duration}
\end{figure}
\clearpage
}
\Cref{fig:round-comms} shows the relationship between the communication cost of the consensus protocol per round and the population size.
The most important aspect is that these results show a linear increase,
which reinforces our analytical result in~\Cref{sec:cons-complexity}.
Note that regardless of whether the transactions are performed with a random neighbour or with a fixed neighbour,
the magnitude of the communication cost is similar.
Both peak at about 100 MB,
which is expected because the consensus protocol is decoupled from the transaction protocol and the validation protocol.
Finally, the rate for which the communication cost increases is higher when the number of facilitators is higher,
which is also expected because the ACS algorithm has a polynomial term w.r.t. $n$ in its communication complexity.

@@

\section{Linear global throughput}

\afterpage{
\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/throughput-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/throughput-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput increases as the population increases when every node transact at the same rate.
  Using fixed neighbours results in a higher throughput because of the caching mechanism.}
  \label{fig:global-throughput}
\end{figure}

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/timeseries}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:backlog-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/timeseries}
    \caption{Transactions are with random neighbours.}
    \label{fig:backlog-random}
  \end{subfigure}
  }
  \caption{Demonstration of the network bottleneck.
  Note that the slope of validated transactions grows at a slower rate in~\Cref{fig:backlog-random} than in~\Cref{fig:backlog-fixed}.}
  \label{fig:backlog}
\end{figure}
\clearpage
}

@@

@@

@@

The same experiment viewed from the perspective of time is shown in~\Cref{fig:facilitators-round-duration}.
Similarly, the duration increases polynomially for a linear increase in fault tolerance.

\afterpage{
\begin{figure}[bt]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/round-communication-cost-vs-facilitators}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:facilitators-round-comms-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/round-communication-cost-vs-facilitators}
    \caption{Transactions are with random neighbours.}
    \label{fig:facilitators-round-comms-random}
  \end{subfigure}
  }
  \caption{The communication cost of the consensus protocol increases polynomially with respect to the number of facilitators as expected from the ACS communication complexity.}
  \label{fig:facilitators-round-comms}
\end{figure}

\begin{figure}[bt]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/round-duration-vs-facilitators}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:facilitators-round-duration-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/round-duration-vs-facilitators}
    \caption{Transactions are with random neighbours.}
    \label{fig:facilitators-round-duration-random}
  \end{subfigure}
  }
  \caption{The consensus duration increases polynomially with respect to the number of facilitators.}
  \label{fig:facilitators-round-duration}
\end{figure}
\clearpage
}
